\section*{Conferences and Courses Attended}

\years{2020} Data Analysis for Metabolic Profiling, Imperial College London. \\
\years{2019} EHNS Head and Neck Robotic Surgery Symposium, Royal College of Physicians, London. \\
\years{2019} Restoration of Dental Implants, BioHorizons at Houston Dental Centre,  Weston-super-Mare. \\
\years{2019} Advanced Placement of Implants, BioHorizons at Houston Dental Centre,  Weston-super-Mare. \\
\years{2019} BAOMS Annual Scientific Meeting, Birmingham. \\
\years{2019} BAHNO Annual Scientific Meeting, Royal College of Physicians, London. \\
\years{2019} Fellows in Training Conference,  Sheffield. \\
\years{2019} Placement of Implants Course, Sheffield. \\
\years{2018} EACMFS Biennial Congress, Munich. \\
\years{2017} Non-technical skills for surgeons, Royal College of Surgeons of Edinburgh. \\
\years{2017} Head and Neck Dissection Course, Keele University. \\
\years{2017} Microvascular Skills Workshop, The Griffin Institute, Northwick Park Hospital. \\
\years{2017} Laser Core of Knowledge, Liverpool University. \\
\years{2017} BAOMS Annual Scientific Meeting, Birmingham. \\
\years{2017} IAOO Congress, Bangalore. \\
\years{2017} BAHNO Annual Scientific Meeting, Royal College of Physicians, London. \\
\years{2016} EACMFS Biennial Congress, London. \\
\years{2016} BAOMS Annual Scientific Meeting, Brighton. \\
\years{2016} BAOMS JTG Conference, Glasgow (Organised and attended). \\
\years{2015} BAOMS Annual Scientific Meeting, Liverpool. \\
\years{2015} BAOMS JTG Conference, Newcastle upon Tyne (Organised and attended). \\
\years{2014} ATLS reverification, Cambridge. \\
\years{2013} BAOMS JTG Conference, London. \\
\years{2012} BAOMS Annual Scientific Meeting, Edinburgh. \\
\years{2012} BAOMS JTG Conference, Edinburgh. \\
\years{2012} ASiT Conference, Cardiff. \\
\years{2012} Art in Surgery workshop, Cardiff. \\
\years{2010} BAOMS JTG Conference, York. \\
\years{2010} ALS, Sunderland. \\
\years{2009} ATLS, Sunderland. \\



