\section*{Appointments Held}

\subsection*{Academic and Management Appointments}

\years{2020--} Deputy Lead, British Association of Oral and Maxillofacial Surgeons (BAOMS) Reconstruction Subspecialty Interest Group.

\years{2019--} Clinical PhD Candidate, Imperial College London.

\years{2019--} Trainee member, National Cancer Research Institute (NCRI) Head and Neck Research Group.

\years{2019--} Trainee member, NCRI Head and Neck Surgery and Localised Therapies Subgroup.

\years{2016--2019} NIHR Academic Clinical Fellow, Institute of Head and Neck Studies and Education (InHANSE), University of Birmingham.

\years{2015--2019} Director, OpenOdontoHub, A Community Interest Company supported by NHS England for the development of open-source electronic dental health record software

\years{2015--2016} Junior Trainee \& Members Representative, BAOMS Council.

\years{2014--2015} President, BAOMS Junior Trainee Group.

\years{2013--15} Journal Club Section Editor, Face Mouth and Jaw Surgery, providing educational analyses of papers for the international trainee journal of OMFS until its closure.

\years{2013--2014} Treasurer, BAOMS Junior Trainee Group.

\years{2009--2010} Treasurer, Sunderland Royal Hospital Doctors' Mess.



\subsection*{Clinical Appointments}

\years{2020--} Clinical Doctoral Fellow, Royal Marsden Hospital, London.

\years{2019--} Clinical Doctoral Fellow, Queen Victoria Hospital, East Grinstead.

\years{2018--2019} OMFS Specialty Trainee, University Hospitals Birmingham.

\years{2017--2018} OMFS Specialty Trainee, Worcester Royal Hospital.

\years{2016--2017} OMFS Specialty Trainee, University Hospitals Birmingham.

\years{2015--2016} OMFS Trust Doctor, Sunderland Royal Hospital.

\years{2011--2015} Emergency Medicine Staff Grade, South Tyneside District Hospital.

\years{2010--2011} Core Surgical Trainee, Hull \& East Yorkshire Hospitals.

\years{2008--2010} Foundation Trainee, Sunderland Royal Hospital.
