\section*{Grants, Awards and Honours}

In total, I have been awarded over half a million pounds in grants and prize money to support my work, and have won academic prizes at local and national levels.

\years{2021} Paul Toller Research Prize---A prestigious prize, awarded for outstanding research in Oral and Maxillofacial Surgery, following an oral presentation of my feasibility trial interim data.

\years{2021} Imperial College London Convergence Science Centre Development Fund---Awarded \pounds47,690 as a co-applicant for a developmental project entitled ``Development of an Ultrafast Infrared Laser System for High Precision Surgery''.

\years{2021} Awarded \pounds1000 by Imperial College London for my `substantial and exceptional achievement' during the Covid-19 pandemic, for my involvement in developing a rapid Covid screening test based on ambient mass spectometry methods.

\years{2021} BAOMS Research Grant---\pounds9,500 awarded for consumables to support my research in intraoperative ambient mass spectrometry for head and neck squamous cell carcinoma margin detection.

\years{2020} NIHR Clinical Doctoral Fellowship---\pounds480,000 awarded as a personal fellowship to deliver a feasibility study to integrate ambient mass spectrometry with transoral robotic surgery for recurrent head and neck squamous cell carcinom, in assocition with Imperial College London and the Royal Marsden Hospital.

\years{2020} Certificate of Commendation---Awarded for presenting the best Clinical Trial Research Proposal at the NIHR CRN ``Tomorrow's Leaders'' Conference 2020.

\years{2018} BAOMS Research Grant---\pounds10,000 awarded for research into lipidomics of head and neck squamous cell carcinoma, in collaboration with the Institute of Head and Neck Cancer Studies and Education and the Phenome Centre Birmingham.

\years{2016--2018} NIHR Academic Clinical Fellowship---A prestigious and competitive programme that rewards ambitious clinicians with outstanding research potiential by placing them on a national specialty training scheme, whilst providing 25\% protected academic time to develop the skills necessary for a career in academic clinical work.

\years{2012} BAOMS Student Bursary--£2000 awarded for an essay entitled “Tissue Engineering Technology and its Possible Applications in OMFS”.

\years{2012--2015} Newcastle University Scholarship---Total of \pounds6,000 awarded as a scholarship over four consecutive years for academic excellence during my Dental degree.

\years{2012} Distinction Year 2 BDS---Awarded for excellence in examinations related to craniofacial biology and development.
