\section*{Presentations}
\subsection*{Oral Presentations}
\begin{itemize}
	\item\textbf{Real time margin analysis of head and neck cancer} Presented at the BAHNO Annual Scientific Meeting in London 2022, for which I was awarded the Best in Session oral presentation prize \textit{(see prizes \& awards section)}.
	\item\textbf{A Better Way to determine tumour margins intraoperatively with ambient mass spectrometry} Presented at the BAOMS Annual Scientific Meeting in Sheffield 2021, presenting interim iKnife data, for which I was awarded the Paul Toller research prize \textit{(see prizes \& awards section)}.
	\item\textbf{Malignant melanoma of the head and neck: does subsite of origin affect prognosis?} Presented at the BAOMS Annual Scientific Meeting in Birmingham 2019. Presenting a retrospective cohort study of melanoma patients, highlighting the importance of anatomical location on margins, and demonstrating that there is no effect on survival.
        \item\textbf{The Prognostic Role Of Surgical Margins In Laser Excision Of Primary Oral Squamous Cell Carcinoma} Presented at EACMFS 2018 in Munich, a cohort study evaluating outcomes following use of surgical laser excision of T1-T2 tumours compared with conventional excision.
        \item\textbf{Next-Generation Sequencing in Head and Neck Cancer} Presenting to the local Oral and Maxillofacial Department on the fundamentals of lipidomics and metabolomics, and the role that these techniques have to play in my research and in cancer research more broadly.
        \item\textbf{Research in OMFS before ST3} Invited to speak to OMFS junior trainees at the Manchester OMFS society conference, May 2018. Gave an interactive lecture for 45 minutes on the reasons for undertaking research, some of the barriers faced by junior trainees, and how they can develop their skills in the field of research at this stage of their careers.
        \item\textbf{Oral Cancer: Trials and Tribulations} MyDentist Clinical Conference, Birmingham, Sep 2017, Invited speaker on behalf of Cancer Research UK, presenting recent developments in diagnosis and management of oral cancer.
        \item\textbf{The Proximal Peroneal Artery Perforator (PPAP) Flap: An Alternative to the Radial Forearm Flap for Head and Neck Reconstruction} \emph{J Higginson}, S Mattine, BAOMS Annual Scientific Meeting, Birmingham, Jun 2017, Presenting outcomes from a novel flap, presenting it as a potential alternative to radial forearm free flap in soft tissue oral reconstruction.
        \item\textbf{The Use of Interpositional Vein Grafts for Free Flap Reconstruction in a Tertiary Head and Neck Unit} \emph{J Higginson}, H Chowlia, T Martin, P Praveen, S Parmar, IAOO Congress, Bangalore, May 2017, Presenting a case series of reconstructions using vein grafts, demonstrating that success rates in our hands were not statistically worse than primarily anastomosed flaps.
        \item\textbf{How reliable are radiological investigations at predicting tumour stage?} N Mahon, A Babbar, \emph{J Higginson}, T Hall, A Lahiri, S Mattine, BAHNO Annual Scientific Meeting, London, May 2017, I performed statistical analysis and interpretation, and helped prepare the presentation of a retrospective analysis comparing radiological tumour staging with pathological staging, which showed a significant but imperfect correlation between the two.
        \item\textbf{The Role of Induction Chemotherapy in Oral Cancer} InHANSE Team Meeting, Birmingham, May 2017, Presented at the local meeting of the Institute of Head and Neck Studies and Education (InHANSE), covering the evidence for induction chemotherapy in oral squamous cell carcinoma.
        \item\textbf{Expression Patterns of Transcription Factors PAX9, SOX2 and SOX9 in Oropharyngeal Squamous Cell Carcinoma} \emph{J Higginson}, H Sathasivam, M Robinson, R Kist, EACMFS Congress, London, Sep 2016, An immunohistochemical study of gene expression, identifying that certain key transciption factors are differentially expressed in HPV positive and HPV negative tumours.
\end{itemize}


\subsection*{Poster Presentations}
\begin{description}
        \item[A Lifeboat in Stormy Seas: A Vein Graft of Last Resort]{\emph{J Higginson}, E Mustafa, K McMillan, N Grew, BAOMS Annual Scientific Meeting, Birmingham, Jun 2017, A case report demonstrating the use of the superficial inferior epigastric artery for vein grafting---previously undescribed in the head and neck}
        \item[Decompression of Cysts: A Comparison of Successful Placement and Compliance]{M Ali, Z Ahmad, \emph{J Higginson}, N Mahon, K McVeigh, T Martin, BAOMS Annual Scientific Meeting}{Birmingham, Jun 2017, An analysis of retention of grommets placed for decompression of benign odontogenic cysts, and associated outcomes}
        \item[Prioritising patient related factors leading to the retention of gastrostomy tubes for over one year in head and neck cancer.]{A Bartram, \emph{J Higginson}, S Owen, P Savage, S Penny, M Nugent, V Paleri, BAHNO Annual Scientific Meeting, London, May 2017, A prospective, semi-quantitative study to identify the factors that patients felt contributed to long-term gastrostomy dependence. The main issues were poor appetite and xerostomia.}
        \item[Are Fascia/Muscle-Only AT Flaps More Likely to Develop Donor Site Seroma]{M Virdi, \emph{J Higginson}, T Martin, P Praveen, S Parmar, IAOO Congress, Bangalore, May 2017, Presenting a case series of ALT reconstructions using retrospective analysis to identify those clinical factors associated with seroma formation.}
\end{description}
