\section*{Teaching}
\begin{description}
	\item[2020, Lecture---BSc Surgical Technology, Imperial College London]{Delivered an online lecture on the role of ambient mass spectrometry in oral and maxillofacial/head and neck cancer surgery, to intercalating medical students undertaking a BSc in surgical technology.}
	\item[2018, Examiner---MBChB Finals]{Examiner on the practical station in the OSCE for finals, May 2018. Attended training and orientation, and shadowed an experienced examiner before taking charge of the station.}
	\item[2017, Seminar---Written Professional Communication]{Final Year MBChB Component, Birmingham Medical School, Dec 2017, Tutor/Assessor, leading small group teaching sessions for final year medical students, enabling and ultimately assessing their ability to write comprehensively and concisely for referrals and discharges.}
	\item[2017, Exam Setting---Human Diseases]{BDS Human Disease Examination, Birmingham School of Dentistry, Aug 2017, Examiner, Attended a meeting to develop new questions for the dental student Human Diseases examination. Recieved training in MCQ setting and the Angoff process. Contributed numerous questions for use in the exam.}
	\item[2016--2019, Lecturer---Tumour Growth, Management \& Prognosis]{Fourth Year BDS Lecture at Birmingham School of Dentistry, lecturing fourth year dental students on aspects of oncology, with a focus on head and neck cancer. Lecture delivered annually from 2016}
	\item[2016-2019, Careers Adviser---West Midlands Dental Deanery]{Regular speaker at careers days, advising trainees on the pathway to oral and maxillofacial surgery.}
\end{description}

